Trauma treatment delay

### 2023-11-09 manuscriptlongversion.Rmd
text
code

The outcome is delayed treatment, which is defined as more than 30
minutes passing from arrival before receiving treatment, as identified
by the multidisciplinary review board and recorded in the trauma care
quality database. The independent variables are gender, patient survival
after 30 days from admission, highest hospital care level, GCS on
arrival, respiratory rate on arrival, systolic blood pressure on
arrival, time from arrival at the hospital until first computed
tomography, if the patient was intubated on arrival and whether they
arrived during weekend or working hours. Those are used as factor
variables. ISS and age are used as continuous variables.

@@

Out of the 11864 patients treated at KS between 2012 and 2022, 1835 were
included in the study. The patient characteristics were as follows in
Table 1.

@@

Out of the 11,864, 5,282 patients were not screened for ofi, which
excludes them from the study. Out of the remaining 6,582 patients, 4,775
patients had missing data in one or more of the analysed parameters,
which led to exclusion from the study.

In the remaining group of 1,835 patients who have been screened for ofi
and have data registered in all parameters examined for the study, 28
patients were found to have received delayed treatment during their stay
at the hospital.

@@

>>>>

The outcome is delayed treatment, which is defined as more than 30
minutes passing from arrival before receiving treatment, as identified
by the multidisciplinary review board and recorded in the trauma care
quality database. The independent variables are gender, highest hospital
care level, GCS on arrival, respiratory rate on arrival, systolic blood
pressure on arrival, if the patient was intubated on arrival, whether
they arrived during weekend or working hours, ISS and age. Of these
variables, GCS, respiratory rate, systolic blood pressure, intubation,
ISS and age are used as continuous variables in the analysis

@@

Out of the 14,022, 5,710 patients were not screened for ofi, which
excludes them from the study. Out of the remaining 8,312 patients, 1,823
patients had missing data in one or more of the analysed parameters,
which led to exclusion from the study.

In the remaining group of 6,489 patients who have been screened for ofi
and have data registered in all parameters examined for the study, 69
patients were found to have received delayed treatment during their stay
at the hospital.

The 6,489 patients included in the study. 68% of the individuals
included were men, with the remaining 32% being women. The mean value
for the ISS score was 10.49, with the standard deviation being 11.4. The
patients had a mean GCS of ... with a standard deviation of ...

@@

@@

![](results.png)
